Decoupled Fallback: A Portable Single-Pass GPU Scan

### 2025-02-26 paper.tex
JDO's MacBook Air M3 has 10 cores

\section{Evaluation}
\subsection{Experimental Setup}
We configure workgroups with a size $w = 256$ threads, where each thread processes $p = 4$ vectors of size 4, resulting in 16 elements per thread and a total work tile size of $t = 4096$. We find a maximum spin count of 4 effectively balances responsiveness to blocking while minimizing false-positive fallbacks. As the size of the local spine is inversely proportional to the subgroup size, we allocate sufficient shared memory to accommodate the WebGPU standard's minimum subgroup size of 4. Due to our overall thriftiness with shared memory, total usage remains modest at only $\sim$1 KB\@. For all tests, we use an input size of $2^{25}$ and an inclusive prefix sum. Our test hardware, listed POSITIONAL-RELATION, spans a wide range of FPG and performance capabilities. We empirically find that Google Chrome's native implementation of WebGPU, Dawn, provides the best performance and use it for all testing, except on the Arm-Mali GPU, which requires Android native, necessitating the use of WGPU\@.\footnote{To keep the perforamance as close to Dawn as possible, we translate our WGSL code with Dawn's Tint transpiler, and provide the raw SPIR-V to WGPU\@.}
\begin{table}
  \centering
  \small
  \begin{tabular*}{\linewidth}{@{\extracolsep{\fill}} l l c r r}
    \toprule
    Vendor & Device Name & LOBE & Occupancy & Subgroup Size \\
    \midrule
    Intel  & HD Graphics 620        & \textbf{Yes} & 9   & 8--32  \\
    ARM    & Mali-G78 MP20          & \textbf{No}  & 40  & 16  \\
    Apple  & M3     (??? Cores)     & \textbf{No}  & 80  & 32  \\
    Apple  & M1 Max (32 Cores)      & \textbf{No}  & 160 & 32  \\
    NVIDIA & GeForce RTX 2080 Super & \textbf{Yes} & 192 & 32  \\
    AMD    & Radeon RX 7900 XT      & \textbf{Yes} & 420 & 32--64  \\
    \bottomrule
  \end{tabular*}
  \caption{Hardware Specifications of Testing Devices.}
  \label{tab:hardware}
\end{table}

>>>>

\section{Evaluation}
\subsection{Experimental Setup}
We configure workgroups with a size $w = 256$ threads, where each thread processes $p = 4$ vectors of size 4, resulting in 16 elements per thread and a total work tile size of $t = 4096$. We find a maximum spin count of 4 effectively balances responsiveness to blocking while minimizing false-positive fallbacks. As the size of the local spine is inversely proportional to the subgroup size, we allocate sufficient shared memory to accommodate the WebGPU standard's minimum subgroup size of 4. Due to our overall thriftiness with shared memory, total usage remains modest at only $\sim$1 KB\@. For all tests, we use an input size of $2^{25}$ and an inclusive prefix sum. Our test hardware, listed POSITIONAL-RELATION, spans a wide range of FPG and performance capabilities. We empirically find that Google Chrome's native implementation of WebGPU, Dawn, provides the best performance and use it for all testing, except on the Arm-Mali GPU, which requires Android native, necessitating the use of WGPU\@.\footnote{To keep the perforamance as close to Dawn as possible, we translate our WGSL code with Dawn's Tint transpiler, and provide the raw SPIR-V to WGPU\@.}
\begin{table}
  \centering
  \small
  \begin{tabular*}{\linewidth}{@{\extracolsep{\fill}} l l c r r}
    \toprule
    Vendor & Device Name & LOBE & Occupancy & Subgroup Size \\
    \midrule
    Intel  & HD Graphics 620        & \textbf{Yes} & 9   & 8--32  \\
    ARM    & Mali-G78 MP20          & \textbf{No}  & 40  & 16  \\
    Apple  & M3     (10 Cores)      & \textbf{No}  & 80  & 32  \\
    Apple  & M1 Max (32 Cores)      & \textbf{No}  & 160 & 32  \\
    NVIDIA & GeForce RTX 2080 Super & \textbf{Yes} & 192 & 32  \\
    AMD    & Radeon RX 7900 XT      & \textbf{Yes} & 420 & 32--64  \\
    \bottomrule
  \end{tabular*}
  \caption{Hardware Specifications of Testing Devices.}
  \label{tab:hardware}
\end{table}
